---
title: "Covid91 vaccine study Final2024"
author: "Michelle Carreno"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="finalSumr2024.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
```

# Introduction

A new  preventative vaccine (covid921) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

## Males
```{r}
table1 <- xtabs(~treatment + sex, data=FinalDat)
rowPerc(table1)
colPerc(table1)
```


```{r}
table1 <- xtabs(~infected + sex, data=FinalDat)
rowPerc(table1)
colPerc(table1)
```

After Looking at the data that was given to me, the placebo was better for the men and the vaccine wasn't that good. In the Covid data it seemed to have effected females more than men even after they got the vaccine. 


## Females

```{r}
table1 <- xtabs(~treatment + sex, data=FinalDat)
rowPerc(table1)
colPerc(table1)
```


```{r}
table1 <- xtabs(~infected + sex, data=FinalDat)
rowPerc(table1)
colPerc(table1)
```

 After Looking at the data that was given to me, the placebo was better for the men and the vaccine wasn't that good. In the Covid data it seemed to have effected females more than men even after they got the vaccine. 



## LGBTQ

```{r}
table1 <- xtabs(~infected + LGBTQ, data=FinalData)
rowPerc(table1)
colPerc(table1) 
```

 LGBTQ it seems that they are doing much better and that nothing is effecting them.   



## Druggies

```{r}
table1 <- xtabs(~infected + DrugUser, data=FinalDat)
rowPerc(table1)
colPerc(table1)
```

 Drug users are mostly liked to get infected by Covid but in this data shown it shows that they are fine and only 8.33 % of drugUser got infected. 

# Overall Results and Conclusions

  Overall it shows that all could get covid but the druguser do way better than normal people. LGBTQ also are most likely to not get infect in any type of way. Weather you get a vaccine or not most of it truly depends on the person.  
